---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE, comment = "#>", fig.path = "man/figures/README-", 
  fig.height = 3, out.width = "100%", dpi = 150, message = FALSE, 
  warning = FALSE, error = FALSE, dev.args = list(type = "cairo")
)
```

# BPRDcolors

**Author:** [Michael McCarthy](https://github.com/mccarthy-m-g)

**License:** [MIT](https://opensource.org/licenses/MIT)

The `BPRDcolours` package provides a collection of color palettes based on Star Trek. It also offers functions for custom palettes and `scale_*` functions for use with `ggplot2`.

## Installation

Install the CRAN release of `BPRDcolours` with

```r
install.packages("BPRDcolours")
```

Install the development version from GitHub with

```r
# install.packages("remotes")
remotes::install_github("mccarthy-m-g/BPRDcolours")
```

## Examples

### Basics

```{r ex1}
library(BPRDcolours)
library(ggplot2)

bprd_pal("hellboy")

bprd_pal("abe")
```

Preview the `hellboy` and `abe` palettes.

```{r ex2}
view_bprd_pals(c("hellboy", "abe"))
```

### Scale functions for use with ggplot2

```{r ex3}
p <- ggplot(iris, aes(Sepal.Width, Sepal.Length, color = Species)) + 
  geom_point(size = 5, alpha = 0.75)
p + scale_colour_bprd() # starfleet is default palette

p <- ggplot(diamonds, aes(carat, stat(count), fill = cut)) +
  geom_density(position = "fill")
p + scale_fill_bprd("hellboy")
p + scale_fill_bprd("abe")
p + scale_fill_bprd("liz")

d <- diamonds[diamonds$cut >= "Very Good", ]
p <- ggplot(d, aes(carat, stat(count), fill = cut)) +
  geom_density(position = "fill")
p + scale_fill_bprd("roger")
```

### All predefined palettes

```{r ex6, fig.width=6, fig.height=8}
# See available palette names
bprd_pal()

# view all predefined palettes
view_bprd_pals()
```
